\documentclass[12pt]{article}
\usepackage{enumitem}

\begin{document}

\section*{n-body-system Requirements}
	\subsection*{Functional Requirements}
		\begin{enumerate}[label=FR-\arabic*]
			\item \label{FR_Initiate} When the user initiates the program, the program {\em shall} parse an input file containing a collection of particles.
			\item \label{FR_Calculate} When a system of particles has been parsed the program {\em shall} calculate the position and velocity of every particle for every time step in accordance with Newton's law of universal gravitation.
			\item \label{FR_TimeAccelerate} When the user specifies a ratio of simulation time to elapsed time the program {\em shall} calculate the number of simulation steps indicated by the ratio every simulation time step.
			\item \label{FR_ViewWindow} When user initiates the program, the program {\em shall} plot the position of each particle on a view window where a multiple of the view window's normal vector summed with the particle vector is orthogonal to the view window.
		\end{enumerate}
	\subsection*{Non-functional Requirements}
		\begin{enumerate}[label=NR-\arabic*]
			\item \label{NF_UsersProvideFile} The program {\em shall} allow users to provide their own system files. 
			\item \label{NF_SystemsProvideG} The program {\em shall} allow system files to provide their own gravitation constant. 
			\item \label{NF_UsersProvideTime} The program  {\em shall} allow users to provide simulation time step sizes. 
			\item \label{NF_DynamicTimeAccelerate} The program {\em shall} dynamically accept user changes to simulation to elapsed time ratio.
			\item \label{NF.FR.DynamicViewWindow} The program {\em shall} dynamically accept user changes to the angles of the view window's normal vector. 
		\end{enumerate}
\end{document}